Identifying Values to Express Emotions with a Non-Anthropomorphic Platform

### 2016-12-06 HRI-LBR/Parts/System-HRI.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

The non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance. The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels. The platform could be observed in Figure~\ref{fig:Robot}. The Arduino Due is in charge to be the interface between the hardware (e.g. motors) and Odroid, which host all the emotion enrichment system.

@@

The main idea of Emotional Enrichment System (EES) is to blend an emotion and a action to produce an "emotional action". However this is not far as previous works have done so far. Therefore, the system has been envisioned to also allow:

@@

In other words, the system could be thought as a box that receives a desire action, action's parameters and emotion to blend them together without paying particular attention on who or how the decision to execute a the particular action was made. This is achieved through the use of messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.  These information are divided into two messages: one for the action and its parameters, and other for the emotion and its intensity. This is done to do not affect the action's execution.

Every time the system receives a new action, it verifies if the action exists and the parameters corresponds to the action. If these two conditions are met, then the system checks if the action is compound or simple. If it is a simple, the system proceeds to add all the required actions (emotive actions) and change their parameters to convey the desired emotion. On the other hand if the action is compound, the action is first decomposed in simple actions (mandatory actions). Each one of these actions is then process to add their emotive actions. However, this addition is done taking in consideration to not add any action that was previously added. Once all the set of simple actions and their parameters are determined, the system proceeds to verify the drivers' existence to execute these actions in the desired platform. If the system finds out that one or more mandatory actions could not be executed, it triggers a message to inform that the desire action could not be executed.

@@

To achieve actions' enrichment with emotions, two different types of actions are used: simple and compound actions. Simple actions are actions that could be considered as ''atomic''; these actions can be enriched with emotion changing their specific parameters. For example, consider two simple actions: speak and move body. The human action of speaking is related to changes in the vocal cords to produce different sounds, while move body is directly related to the body movement. Therefore, for the speaking action the following parameters are expected: text, pitch and tone. On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints. Since each action is characterized by different parameters, the parameters' modifications to obtain an emotional action will be different for each of them. On the other hand, compound action is an action created from other compound or simple actions. For example, suppose that it is required that the robot has to \textit{recite} some dialogue and \textit{walk} to a different position, as doing a trajectory. A possible implementation could consist on speak simple action in parallel to two consecutive action walk, which is also a compound action that is composed by three parallel actions: balance left arm, balance right arm, and move body.

@@

	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received. The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described in the message. This parameters' verification is done on the implemented description for each simple action, which describes the parameters that are mandatory and those that are optional. When the verification is done, and all the action exists and  the parameters correspond, an $ext$ is created.

	\item \textit{Emotion addition:} uses the $ext$ created in the previous phase. In this phase new simple actions are added to the $ext$ and the simple action's parameters are modified following the emotion description, which is loaded from files. This process is broken down in two steps. First, all actions that are required to convey the desired emotion, and that are not yet present in the branch are added. Second, the emotional parameters are modulated based on the emotion's intensity and character traits.

	\item \textit{Execution:} this is the last phase and it is done after the $ext$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters). The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution. In this phase is maintain a reference to the mandatory and emotional action, thus when a new emotion is received the system stops the previous emotional action and start executing the new ones without affecting the general execution of the actions.

>>>>

A non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance. The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels. The platform could be observed in Figure~\ref{fig:Robot}. The Arduino Due is in charge to be the interface between the hardware (e.g. motors) and Odroid, which host all the Emotion Enrichment System.

@@

The main idea of Emotional Enrichment System is to blend an emotion and a action to generate the effect of "emotional action". However this is not far as previous works have done so far. Therefore, the system has been envisioned to also enable:

@@

In other words, the system could be thought as a black box that receives a desire action, action's parameters and emotion to blend them together without paying particular attention on who or how the decision to execute a particular action was made. This is achieved through the use of messages to describe the action that should be executed, as well its parameters, emotion and emotion's intensity.  These information are divided into two messages: one for the action and its parameters, and other for the emotion and its intensity. This is done to do not affect the action's execution.

Every time the system receives a new action, it verifies if the action exists and parameters corresponds to the desire action. If these two conditions are met, then the system checks if the action is compound or simple. If it is a simple, the system proceeds to add all the required actions (emotional actions) and change their parameters to convey the desired emotion. On the other hand if the action is compound, the action is first decomposed in simple actions (mandatory actions). Each one of these actions is then process to add their emotional actions. However, this addition is done taking in consideration to not add any action that was previously added. Once all the set of simple actions and their parameters are determined, the system proceeds to verify the drivers' existence to execute these actions in the desired platform. If the system finds out that one or more mandatory actions could not be executed, it triggers a message to inform that the desire action could not be executed.

@@

To achieve actions' enrichment with emotions, two different types of actions are used: simple and compound actions. Simple actions are actions that could be considered as ''atomic''; these actions can be enriched with emotion changing their specific parameters. For example, consider two simple actions: speak and move body. The human action of speaking is related to changes in the vocal cords to produce different sounds, while move body is directly related to the body movement. Therefore, for the speaking action the following parameters are expected: text, pitch and tone. On the other hand, the action move body would have as parameters the desired destination, velocity, and trajectory constraints. Since each action is characterized by different parameters, parameters' modifications to obtain an emotional action will be different for each of them. On the other hand, compound action is an action created from other compound or simple actions. For example, suppose that it is required that the robot has to \textit{recite} some dialogue and \textit{walk} to a different positions, as doing a trajectory. A possible implementation could consist on speak simple action in parallel to two consecutive action walk, which is also a compound action that is composed by three parallel actions: balance left arm, balance right arm, and move body.

@@

	\item \textit{Generation of emotional execution tree:} this phase starts every time that a new action message is received. The process begins by parsing the format, verifying that the actions described on it exist in the system, and that the parameters correspond to the ones expected by each action described in the message. This parameters' verification is done on the implemented description for each simple action, which describes the parameters that are mandatory and those that are optional. When the verification is done, and all the action exists and  the parameters correspond, an $EXT$ is created.

	\item \textit{Emotion addition:} uses the $EXT$ created in the previous phase. In this phase new simple actions are added to the $EXT$ and the simple action's parameters are modified following emotions' descriptors, which are loaded from files. This process is broken down in two steps. First, all actions that are required to convey the desired emotion, and that are not yet present in the branch are added. Second, the emotional parameters are modulated based on the emotion's intensity and character traits.

	\item \textit{Execution:} this is the last phase and it is done after the $EXT$ is ''coloured'' with emotional characteristics (actions additions and emotional parameters). The decision to have two different communication channels, one for action parameters and another for the action emotional parameters, was taken to enable the possibility to update the emotional parameters without interfering with the current execution. In this phase is maintain a reference to the mandatory and emotional action, thus when a new emotion is received the system stops the previous emotional action and start executing the new ones without affecting the general execution of the actions.

### 2016-12-06 JournalIJSR/IJSR.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

\institute{Julian M. Angel-Fernandez \at
              Automation and Control Institute, Vienna University of Technology,\\ Karlsplatz 13, 1040 Vienna, Austria \\
              Tel.: +43-158801\\
              \email{jangelfe@tuwien.ac.at}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Andrea Bonarini \at
              Andrea Bonarini, Dipartimento di Elettronica, Informazione e Bioingegneria,Politecnico di Milano,\\
              Piazza Leonardo da Vinci 32, 20133 Milan, Italy \\
              \email{andrea.bonarini@polimi.it}
}

@@

\begin{abstract}
Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that cannot have a humanoid shape, and still have to interact with humans. As a consequence,  features not related with shape should be exploited to support robot acceptance. This paper presents an experiment made to understand the contribution to humans' perception of emotion of angular and linear velocity, body orientation, and movement direction of a non-anthropomorphic robot. A top 10 table of feature values combination was created for each enlisted emotion using alpha agreement for the whole treatment and for the desired emotion. The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
\keywords{Robot-Human Interaction \and Emotion Projection}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

\institute{Julian M. Angel-Fernandez \at
              Automation and Control Institute, Vienna University of Technology,\\ Karlsplatz 13, 1040 Vienna, Austria \\
              Tel.: +43-158801\\
              \email{julian.angel.fernandez@tuwien.ac.at}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Andrea Bonarini \at
              Andrea Bonarini, Dipartimento di Elettronica, Informazione e Bioingegneria,Politecnico di Milano,\\
              Piazza Leonardo da Vinci 32, 20133 Milan, Italy \\
              \email{andrea.bonarini@polimi.it}
}

@@

\begin{abstract}
Social environments are intricate spaces where people behave in ways that are socially accepted. In a similar way, robots that interact with humans on daily bases are expected to develop certain behaviours to be socially accepted by people. This creates the necessity to make robots with high social presence that let humans to feel comfortable with their presence. The straightest way to fulfill is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics. As a consequence many social robots have been built with anthropomorphic embodiment, which could include features to express emotions. Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that not required anthropomorphic shape due to the nature of the tasks that they have to perform. As a consequence,  features not related with anthropomorphic embodiment should be exploited to support robot acceptance. This paper presents an experiment made to understand humans' perception of emotion for angular and linear velocity, body orientation, and movement direction. Therefore, a non-anthropomorphic platform was used in the experiments to let participants to focus on the desired features. Moreover a Likert questionnaire was used to measure participants' perception for different treatments. The Krippendorff's alpha agreement was used to create a top 10 table for each of the emotions listed in the questionnaire. The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
\keywords{Human-Robot Interaction \and Emotion Expression \and Experiment \and Non-anthropomorphic Platform \and Emotions Expression with Non-anthropomorphic Platform}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

### 2016-12-06 JournalIJSR/Parts/Conclusion.tex
Changes in international studies has been changed as it was informed. The IJSR: intro and related work was modify. It was added a HRI late breaking report that was submitted to HRI

This paper presented an experiment made to understand the contribution of angular and linear velocity, body's orientation, and movement direction on humans' perception of emotion expression by a non-anthropomorphic platform. The emotions covered in this experiment correspond to four of the ones enlisted by Ekman~\cite{Ekman2001} as basic emotions: anger, happiness, fear and sadness. To study the contribution of the desired features, a non-anthropomorphic, holonomic platform was used. The experiment was conducted at Politecnico di Milano, and involved 49 participants, each exposed to 20 over 195 movements, selected randomly for each participant. The Krippendorff's alpha agreement~\cite{Krippendorff2007} was used to calculate the consensus about the interpretation of each treatment. Using  alpha and the average emotion intensity attributed to each movement a top 10 movement table for each of the emotions was created.

>>>>

This paper presented an experiment made to understand the contribution of angular and linear velocity, body's orientation, and movement direction on humans' perception of emotion expression by a non-anthropomorphic platform. The emotions covered in this experiment correspond to four of the ones enlisted by Ekman~\cite{Ekman2001} as basic emotions: \textit{Anger}, \textit{Happiness}, \textit{Fear} and \textit{Sadness}. To study the contribution of the desired features, a non-anthropomorphic, holonomic platform was used. The experiment was conducted at Politecnico di Milano, and involved 49 participants, each exposed to 20 over 195 movements, selected randomly for each participant. The Krippendorff's alpha agreement~\cite{Krippendorff2007} was used to calculate the consensus about the interpretation of each treatment. Using  alpha and the average emotion intensity attributed to each movement a top 10 movement table for each of the emotions was created.
